Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-08-09 manuscript/main.tex
R1 point 2

>>>>

While we did not identify any statistical associations between individual species
and cognitive performance in our youngest subset (0 to 6 months),
it may be because brain developmental trajectories begin \textit{in utero},
and microbial influences (that can only begin at birth)
take additional time to manifest.
Future studies should attempt to link early-life microbial exposures
to future cognitive performance or brain development.
